\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\usepackage{xpatch}
\moderncvcolor{black} % Subtle, classic color
\AtBeginDocument{\definecolor{color2}{rgb}{0,0,0}} % Force first name black
\usepackage[letterpaper, margin=0.6in]{geometry}
\usepackage{xcolor} % Ensure color support
\usepackage{graphicx} % Support for images
\usepackage{fontspec} % Support for Unicode characters
\setmainfont{Times New Roman} % Set English font
\pagenumbering{arabic} % Ensure page numbering is defined
\usepackage[unicode]{hyperref} % Load hyperref after setting page numbering
\sloppy % Allow LaTeX to relax spacing issues
\usepackage{enumitem} % Allows list customization

\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

%==================== PERSONAL INFO ====================%
\name{\textcolor{black}{Saeyoung}}{Kim}
\address{Cambridge, MA, USA}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}
\social[github]{PrimaryAnomaly}

\begin{document}

\makecvtitle
\vspace{-3em}

%==================== SUMMARY ====================%
\section{Professional Summary}
Systems engineer with 9+ years of experience in space hardware development, system integration, and verification across satellite and embedded payload programs. Led systems engineering and integration (SE\&I) activities for military satellite programs including requirements definition, architecture decomposition, integrated test planning, and verification and validation. Designed and validated CubeSat payload systems from concept of operations through flight-ready hardware. Skilled in cross-functional coordination, stakeholder communication, and delivering complex technical outcomes in fast-moving environments.

\section{Technical Skills}
\begin{minipage}[t]{0.48\textwidth}
\cvitem{SE\&I}{Requirements Management, Architecture Definition, V\&V Planning}
\cvitem{Hardware}{System Integration, Functional/Performance Testing, AIT}
\cvitem{Electronics}{Circuit Design, PCB Layout, Embedded Sensors}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Software}{Python, C/C++, MATLAB, Git, Linux}
\cvitem{CAD/Fabrication}{Fusion360, AutoCAD, KiCad, 3D Printing, CNC}
\cvitem{Methods}{Systems Engineering Lifecycle, Test Planning, Anomaly Resolution}
\end{minipage}

%==================== EXPERIENCE ====================%
\section{Professional Experience}

\cventry{2025.07--Present}{\textbf{Postdoctoral Associate} | Process Systems Engineering and Modeling}{University of Massachusetts Lowell}{Lowell, MA, USA}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Developed system-level digital twin framework integrating physics-based modeling with statistical process control
    \item Led real-time quality monitoring system development, validating 100+ pharmaceutical production batches
    \item Defined system requirements and coordinated deliverables across engineering and research stakeholders
    \item Led technical deliverables for government-funded collaboration, managing cross-functional coordination
\end{itemize}}

\cventry{2024.02--2025.05}{\textbf{Systems Integration Engineer} | Satellite SE\&I and Integration Testing}{Hanwha Systems}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Led systems engineering and integration activities for military SAR satellite programs across full development lifecycle
    \item Defined, decomposed, and managed subsystem-level requirements for integrated electrical systems
    \item Developed and executed Integrated Systems Test (IST) plans for Flight Model assembly through acceptance testing
    \item Designed Electrical Ground Support Equipment (EGSE) architecture and coordinated integration test configurations
    \item Monitored design and testing progress, communicated potential issues and change impacts to SE\&I leadership
    \item Diagnosed system-level anomalies during integration testing and recommended corrective actions
    \item Coordinated across subsystem engineers, program office, and external stakeholders for SE\&I planning and execution
    \item Contributed to architecture definition for a high-throughput satellite manufacturing facility
\end{itemize}}

%==================== EDUCATION ====================%
\section{Education}
\cventry{2017.03--2024.02}{\textbf{PhD in Electrical Engineering} | CubeSat Payload Systems Engineering}{Korea University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Secured and managed \$220K research grant for CubeSat biological payload system development
    \item Defined concept of operations, system architecture, and subsystem requirements for biological CubeSat payload
    \item Designed, integrated, and validated multi-modal sensor suite from concept through functional verification
    \item Developed embedded firmware in C/C++ for real-time data acquisition and autonomous system operation
    \item Executed verification and validation of pressurized fluidic and thermal management subsystems
    \item Coordinated across research teams and stakeholders to deliver integrated payload hardware
    \item Published 2 first-author and 6 co-authored journal papers on electrochemical sensors, space payloads, and embedded systems
\end{itemize}}

\cventry{2013.03--2017.02}{\textbf{BSc in Mechanical Engineering}}{Konkuk University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Conducted research in electrochemical sensor fabrication, hardware prototyping, and system validation
    \item Gained experience in CAD modeling, mechanical design, PCB prototyping, and precision measurement
\end{itemize}}

%==================== PUBLICATIONS ====================%
\section{Publications}
\subsection{Journal Publications}
\begin{sloppypar} % Prevents underfull box errors
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textbf{\underline{Saeyoung Kim}}, Jaewon Lee, Kimia Babaei, Seonkgyu Yoon, "Digital Twins in Lyophilization: Advances in Pharmaceutical Process Development and Optimization," \textit{Biotechnology Advances}, 2026. (Manuscript in Preparation, Target Submission: Q1 2026)
    \item Jinhwee Kil, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "Investigation of thermal management strategies for biological CubeSat payloads," Acta Astronautica, 2024, Art. no. 228. DOI: 10.1016/j.actaastro.2024.11.059.
    \item \textbf{\underline{Kim, S.}}; Park, S.; Pak, J.J., "Multi-Modal Multi-Array Electrochemical and Optical Sensor Suite for a Biological CubeSat Payload," MDPI Sensors, 2024, 24, Art. no. 265. DOI: 10.3390/s24010265.
    \item Ji-Hoon Han, Sang Hyun Park, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "A Performance Improvement of Enzyme-Based Electrochemical Lactate Sensor Fabricated by Electroplating Novel PdCu Mediator on a Laser Induced Graphene Electrode," Bioelectrochemistry, 2022, 148, 108259. DOI: 10.1016/j.bioelechem.2022.108259.
    \item \textbf{\underline{Saeyoung Kim}}, Ji-Hoon Han, Beelee Chua, James Jungho Pak, "A pH Sensing Pipette for Cross-Contamination Prevention in Industrial Fermentation," IEEE Transactions on Industrial Electronics, 2022, 69(7), 7461-7469. DOI: 10.1109/TIE.2021.3099251.
    \item S.D. Raut, N.M. Shinde, B.G. Ghule, \textbf{\underline{S. Kim}}, J.J. Pak, Q. Xia, R.S. Mane, "Room-Temperature Solution Processed Sharp-Edged Nanoshapes of," Chemical Engineering Journal, 2022, 433(2), 133627. DOI: 10.1016/j.cej.2021.133627.
    \item S.E. Jeong, \textbf{\underline{S. Kim}}, J.H. Han, J. Jungho Pak, "Simple Laser-Induced Graphene Fiber Electrode Fabrication for High-Performance Heavy-Metal Sensing," Microchemical Journal, 2022, 172, 106950. DOI: 10.1016/j.microc.2021.106950.
    \item Sanghoon Cho, Jungmo Jung, \textbf{\underline{Saeyoung Kim}}, James Pak, "Conduction Mechanism and Synaptic Behaviour of Interfacial Switching AlO$\sigma$-based RRAM," Semiconductor Science and Technology, 2020, 35(8), 085006. DOI: 10.1088/1361-6641/ab8d0e.
    \item Ji-Hoon Han, \textbf{\underline{Saeyoung Kim}}, Jaesung Choi, Sora Kang, Youngmi Kim Pak, James Jungho Pak, "Development of Multi-Well-Based Electrochemical Dissolved Oxygen Sensor Array," Sensors and Actuators B: Chemical, 2020, 306, 127465. DOI: 10.1016/j.snb.2019.127465.
\end{itemize}
\end{sloppypar}

\subsection{Conference Presentations}
\begin{sloppypar}
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textit{Thermal Management System for a Fluidic Card in a Small Satellite Biological Payload}, Korean Institute of Electrical Engineers (KIEE) Autumn Conference, 2022.
    \item \textit{A Pipette with an Integrated pH Sensor for Liquid Sampling Applications}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2019.
    \item \textit{IoT System for Monitoring pH, Dissolved Oxygen, Temperature, and Electrical Conductivity in Liquids}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2018.
    \item \textit{Development Trends of Non-Invasive Glucose Sensor Technology}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2017.
\end{itemize}
\end{sloppypar}

\subsection{Seminar Presentations}
\begin{itemize}[leftmargin=0.5cm, itemsep=2pt, parsep=1pt]
    \item \textit{Bioprocessing in Space: Challenges and Opportunities for Pharmaceutical Manufacturing Beyond Earth}, Lowell Center for Space Science and Technology (LoCSST), UMass Lowell, 2025.
\end{itemize}

\vfill
\centering{References available upon request.}

\end{document}
