\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\usepackage{xpatch}
\moderncvcolor{black} % Subtle, classic color
\AtBeginDocument{\definecolor{color2}{rgb}{0,0,0}} % Force first name black
\usepackage[letterpaper, margin=0.6in]{geometry}
\usepackage{xcolor} % Ensure color support
\usepackage{graphicx} % Support for images
\usepackage{fontspec} % Support for Unicode characters
\setmainfont{Times New Roman} % Set English font
% \newfontfamily\koreanfont{Noto Sans CJK KR} % Korean font (uncomment if needed)
\pagenumbering{arabic} % Ensure page numbering is defined
\usepackage[unicode]{hyperref} % Load hyperref after setting page numbering
\sloppy % Allow LaTeX to relax spacing issues
\usepackage{enumitem} % Allows list customization

\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

%==================== PERSONAL INFO ====================%
\name{\textcolor{black}{Saeyoung}}{Kim}
\address{Cambridge, MA, USA}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}
\social[github]{PrimaryAnomaly}

\begin{document}

\makecvtitle
\vspace{-3em}

%==================== SUMMARY ====================%
\section{Professional Summary}
Driven by developing resilient, autonomous infrastructure for first-generation Mars colonies. Experienced in embedded systems, sensor integration, hardware/software co-design, PCB development, and system architecture, with skills in sensing, actuation, and communications integration using MATLAB, Python, and C/C++. Previously an Electronic Design Integration and Assembly, Integration, and Testing (AIT) Engineer at Hanwha Systems, handling systems integration, performance validation, and EM/QM/FM test campaigns for military SAR satellites. Currently a postdoctoral researcher at UMass Lowell developing digital twin frameworks with MSPC for real-time monitoring in mRNA-LNP vaccine manufacturing, building process control foundations for life-critical systems in extreme environments.

\section{Technical Skills}
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Programming}{Python, C/C++, MATLAB}
\cvitem{CAD/CAM}{Fusion360, AutoCAD, KiCad}
\cvitem{Hardware}{Jigs, PCB, Embedded, Systems Integration}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Fabrication}{3D Printing, Laser Cutting, CNC}
\cvitem{DevOps}{Git, Docker, Linux}
\cvitem{Methods}{Space Hardware AIT, Freezedrying, MSPC}
\end{minipage}

%==================== EXPERIENCE ====================%
\section{Professional Experience}

\cventry{2025.07--Present}{\textbf{Postdoctoral Associate} | Freeze-drying Modeling and Process Control Software Development}{University of Massachusetts Lowell}{Lowell, MA, USA}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Developed digital twin framework integrating physics-based modeling with MSPC for pharmaceutical manufacturing
    \item Led real-time quality monitoring system development for mRNA-LNP vaccine production, analyzing 100+ batches
    \item Built Python software suite replacing commercial platforms (gPROMS, SIMCA) for reproducible process development
    \item Designed end-to-end data pipeline for multi-day batch cycles with automated quality prediction
    \item Co-authoring high-impact journal manuscripts (IF 10+); leading deliverables for government-funded collaboration
\end{itemize}}

\cventry{2024.02--2025.05}{\textbf{Systems Integration Engineer} | Satellite Systems Design \& Integration and Testing}{Hanwha Systems}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Led system integration and validation of military SAR satellites.  
    \item Developed and executed Electric Test Bed (ETB) test procedures for performance and integration.  
    \item Defined and executed test plans for embedded systems and communications.  
    \item Designed high-level Electrical Ground Support Equipment (EGSE) architecture and integration test plans.  
    \item Developed electrical Integrated Systems Test (IST) plans for Flight Model Assembly, Integration, and Testing.  
    \item Diagnosed and resolved hardware/software interactions in networked systems.  
    \item Contributed to designing a high-throughput satellite manufacturing facility. 
\end{itemize}}

%==================== EDUCATION ====================%
\section{Education}
\cventry{2017.03--2024.02}{\textbf{PhD in Electrical Engineering} | CubeSat Embedded Systems \& Sensor Integration}{Korea University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Secured and managed 300M KRW (\$220K) research grant for CubeSat biological payload R\&D
    \item Designed and fabricated multi-modal electrochemical and optical sensor suite for space applications
    \item Developed MCU firmware in C/C++ for real-time sensor data acquisition and autonomous operation
    \item Built and validated embedded system prototypes including circuit design, PCB layout, and system integration
    \item Debugged complex hardware/software interactions in networked electromechanical devices
    \item Published 3 first-author SCI papers (cumulative IF: 17.4) and co-authored 10+ publications
\end{itemize}}

\cventry{2013.03--2017.02}{\textbf{BSc in Mechanical Engineering}}{Konkuk University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Conducted research at the Smart Materials Nano Lab, focusing on electrochemical sensor development.
    \item Gained hands-on experience in CAD modeling, PCB prototyping, microfabrication, and academic writing.
\end{itemize}}

%==================== PUBLICATIONS ====================%
\section{Publications}
\subsection{Journal Publications}
\begin{sloppypar} % Prevents underfull box errors
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textbf{\underline{Saeyoung Kim}}, Jaewon Lee, Kimia Babaei, Seonkgyu Yoon, "Digital Twins in Lyophilization: Advances in Pharmaceutical Process Development and Optimization," \textit{Biotechnology Advances}, 2026. (Manuscript in Preparation, Target Submission: Q1 2026)
    \item Jinhwee Kil, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "Investigation of thermal management strategies for biological CubeSat payloads," Acta Astronautica, 2024, Art. no. 228. DOI: 10.1016/j.actaastro.2024.11.059.
    \item \textbf{\underline{Kim, S.}}; Park, S.; Pak, J.J., "Multi-Modal Multi-Array Electrochemical and Optical Sensor Suite for a Biological CubeSat Payload," MDPI Sensors, 2024, 24, Art. no. 265. DOI: 10.3390/s24010265.
    \item Ji-Hoon Han, Sang Hyun Park, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "A Performance Improvement of Enzyme-Based Electrochemical Lactate Sensor Fabricated by Electroplating Novel PdCu Mediator on a Laser Induced Graphene Electrode," Bioelectrochemistry, 2022, 148, 108259. DOI: 10.1016/j.bioelechem.2022.108259.
    \item \textbf{\underline{Saeyoung Kim}}, Ji-Hoon Han, Beelee Chua, James Jungho Pak, "A pH Sensing Pipette for Cross-Contamination Prevention in Industrial Fermentation," IEEE Transactions on Industrial Electronics, 2022, 69(7), 7461-7469. DOI: 10.1109/TIE.2021.3099251.
    \item S.D. Raut, N.M. Shinde, B.G. Ghule, \textbf{\underline{S. Kim}}, J.J. Pak, Q. Xia, R.S. Mane, "Room-Temperature Solution Processed Sharp-Edged Nanoshapes of," Chemical Engineering Journal, 2022, 433(2), 133627. DOI: 10.1016/j.cej.2021.133627.
    \item S.E. Jeong, \textbf{\underline{S. Kim}}, J.H. Han, J. Jungho Pak, "Simple Laser-Induced Graphene Fiber Electrode Fabrication for High-Performance Heavy-Metal Sensing," Microchemical Journal, 2022, 172, 106950. DOI: 10.1016/j.microc.2021.106950.
    \item Sanghoon Cho, Jungmo Jung, \textbf{\underline{Saeyoung Kim}}, James Pak, "Conduction Mechanism and Synaptic Behaviour of Interfacial Switching AlOσ-based RRAM," Semiconductor Science and Technology, 2020, 35(8), 085006. DOI: 10.1088/1361-6641/ab8d0e.
    \item Ji-Hoon Han, \textbf{\underline{Saeyoung Kim}}, Jaesung Choi, Sora Kang, Youngmi Kim Pak, James Jungho Pak, "Development of Multi-Well-Based Electrochemical Dissolved Oxygen Sensor Array," Sensors and Actuators B: Chemical, 2020, 306, 127465. DOI: 10.1016/j.snb.2019.127465.
\end{itemize}
\end{sloppypar}

\subsection{Conference Presentations}
\begin{sloppypar}
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textit{Thermal Management System for a Fluidic Card in a Small Satellite Biological Payload}, Korean Institute of Electrical Engineers (KIEE) Autumn Conference, 2022.
    \item \textit{A Pipette with an Integrated pH Sensor for Liquid Sampling Applications}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2019.
    \item \textit{IoT System for Monitoring pH, Dissolved Oxygen, Temperature, and Electrical Conductivity in Liquids}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2018.
    \item \textit{Development Trends of Non-Invasive Glucose Sensor Technology}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2017.
\end{itemize}
\end{sloppypar}

\subsection{Seminar Presentations}
\begin{itemize}[leftmargin=0.5cm, itemsep=2pt, parsep=1pt]
    \item \textit{Bioprocessing in Space: Challenges and Opportunities for Pharmaceutical Manufacturing Beyond Earth}, Lowell Center for Space Science and Technology (LoCSST), UMass Lowell, 2025.
\end{itemize}

\vfill
\centering{References available upon request.}

\end{document}
