\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\usepackage{xpatch}
\moderncvcolor{black} % Subtle, classic color
\AtBeginDocument{\definecolor{color2}{rgb}{0,0,0}} % Force first name black
\usepackage[letterpaper, margin=0.6in]{geometry}
\usepackage{xcolor} % Ensure color support
\usepackage{graphicx} % Support for images
\usepackage{fontspec} % Support for Unicode characters
\setmainfont{Times New Roman} % Set English font
% \newfontfamily\koreanfont{Noto Sans CJK KR} % Korean font (uncomment if needed)
\pagenumbering{arabic} % Ensure page numbering is defined
\usepackage[unicode]{hyperref} % Load hyperref after setting page numbering
\sloppy % Allow LaTeX to relax spacing issues
\usepackage{enumitem} % Allows list customization

\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

%==================== PERSONAL INFO ====================%
\name{\textcolor{black}{Saeyoung}}{Kim}
\address{Cambridge, MA, USA}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}
\social[github]{PrimaryAnomaly}

\begin{document}

\makecvtitle
\vspace{-3em}

%==================== SUMMARY ====================%
\section{Professional Summary}
Hardware-software integration engineer with hands-on experience building embedded systems from concept to deployment. Designed and fabricated multi-modal sensor systems, developed real-time MCU firmware in C/C++, and integrated complex electromechanical subsystems for space-qualified hardware. Led end-to-end development cycles spanning circuit design, PCB layout, firmware development, and system validation. Background in satellite systems integration provides direct experience debugging hardware/software interactions in networked systems under communication constraints—directly applicable to multi-agent robotic coordination.

\section{Technical Skills}
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Programming}{Python, C/C++, MATLAB, Git}
\cvitem{Embedded}{MCU Firmware, Real-time Systems}
\cvitem{Electronics}{Circuit Design, PCB Layout, Sensors}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Fabrication}{3D Printing, Laser Cutting, CNC, Soldering}
\cvitem{CAD}{Fusion360, AutoCAD, SolidWorks}
\cvitem{Systems}{Satellite AIT, Hardware Testing}
\end{minipage}

%==================== EXPERIENCE ====================%
\section{Professional Experience}

\cventry{2025.07--Present}{\textbf{Postdoctoral Associate} | Process Modeling \& Software Development}{University of Massachusetts Lowell}{Lowell, MA, USA}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Architected Python software suite with GUI replacing commercial platforms (gPROMS, SIMCA)
    \item Developed mechanistic models integrating physics simulation with real-time sensor data
    \item Built digital twin framework coupling physics simulation with multivariate state monitoring and prediction
    \item Developed predictive models for critical process outcomes using multivariate sensor data
    \item Designed end-to-end data pipeline processing multi-sensor streams from 100+ manufacturing batches
    \item Led software architecture decisions for modular, maintainable codebase
\end{itemize}}

\cventry{2024.02--2025.05}{\textbf{Systems Integration Engineer} | Satellite Systems Integration \& Validation}{Hanwha Systems}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Led system integration and validation of military SAR satellites across EM/QM/FM test campaigns
    \item Designed Electrical Ground Support Equipment (EGSE) architecture for automated hardware testing
    \item Developed Electric Test Bed (ETB) procedures validating embedded systems and communication interfaces
    \item Diagnosed and resolved hardware/software interaction failures in networked subsystems
    \item Defined electrical Integrated Systems Test (IST) plans for Flight Model AIT
    \item Contributed to high-throughput satellite manufacturing facility design with automated test infrastructure
\end{itemize}}

%==================== EDUCATION ====================%
\section{Education}
\cventry{2017.03--2024.02}{\textbf{PhD in Electrical Engineering} | Embedded Systems \& Hardware Integration}{Korea University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Designed and fabricated multi-modal sensor suite (electrochemical, optical) for autonomous space operation
    \item Developed MCU firmware in C/C++ for real-time data acquisition with sub-millisecond timing constraints
    \item Built embedded prototypes end-to-end: circuit schematic, PCB layout, assembly, firmware, system validation
    \item Integrated thermal management, power distribution, and communication subsystems for CubeSat payload
    \item Debugged complex hardware/software interactions in networked electromechanical systems
    \item Secured and managed 300M KRW (\$220K) research grant for biological payload R\&D
    \item Published 3 first-author SCI papers (cumulative IF: 17.4) and co-authored 10+ publications
\end{itemize}}

\cventry{2013.03--2017.02}{\textbf{BSc in Mechanical Engineering}}{Konkuk University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Conducted research at the Smart Materials Nano Lab, focusing on electrochemical sensor development.
    \item Gained hands-on experience in CAD modeling, PCB prototyping, microfabrication, and academic writing.
\end{itemize}}

%==================== PUBLICATIONS ====================%
\section{Publications}
\subsection{Journal Publications}
\begin{sloppypar} % Prevents underfull box errors
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textbf{\underline{Saeyoung Kim}}, Jaewon Lee, Kimia Babaei, Seonkgyu Yoon, "Digital Twins in Lyophilization: Advances in Pharmaceutical Process Development and Optimization," \textit{Biotechnology Advances}, 2026. (Manuscript in Preparation, Target Submission: Q1 2026)
    \item Jinhwee Kil, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "Investigation of thermal management strategies for biological CubeSat payloads," Acta Astronautica, 2024, Art. no. 228. DOI: 10.1016/j.actaastro.2024.11.059.
    \item \textbf{\underline{Kim, S.}}; Park, S.; Pak, J.J., "Multi-Modal Multi-Array Electrochemical and Optical Sensor Suite for a Biological CubeSat Payload," MDPI Sensors, 2024, 24, Art. no. 265. DOI: 10.3390/s24010265.
    \item Ji-Hoon Han, Sang Hyun Park, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "A Performance Improvement of Enzyme-Based Electrochemical Lactate Sensor Fabricated by Electroplating Novel PdCu Mediator on a Laser Induced Graphene Electrode," Bioelectrochemistry, 2022, 148, 108259. DOI: 10.1016/j.bioelechem.2022.108259.
    \item \textbf{\underline{Saeyoung Kim}}, Ji-Hoon Han, Beelee Chua, James Jungho Pak, "A pH Sensing Pipette for Cross-Contamination Prevention in Industrial Fermentation," IEEE Transactions on Industrial Electronics, 2022, 69(7), 7461-7469. DOI: 10.1109/TIE.2021.3099251.
    \item S.D. Raut, N.M. Shinde, B.G. Ghule, \textbf{\underline{S. Kim}}, J.J. Pak, Q. Xia, R.S. Mane, "Room-Temperature Solution Processed Sharp-Edged Nanoshapes of," Chemical Engineering Journal, 2022, 433(2), 133627. DOI: 10.1016/j.cej.2021.133627.
    \item S.E. Jeong, \textbf{\underline{S. Kim}}, J.H. Han, J. Jungho Pak, "Simple Laser-Induced Graphene Fiber Electrode Fabrication for High-Performance Heavy-Metal Sensing," Microchemical Journal, 2022, 172, 106950. DOI: 10.1016/j.microc.2021.106950.
    \item Sanghoon Cho, Jungmo Jung, \textbf{\underline{Saeyoung Kim}}, James Pak, "Conduction Mechanism and Synaptic Behaviour of Interfacial Switching AlOσ-based RRAM," Semiconductor Science and Technology, 2020, 35(8), 085006. DOI: 10.1088/1361-6641/ab8d0e.
    \item Ji-Hoon Han, \textbf{\underline{Saeyoung Kim}}, Jaesung Choi, Sora Kang, Youngmi Kim Pak, James Jungho Pak, "Development of Multi-Well-Based Electrochemical Dissolved Oxygen Sensor Array," Sensors and Actuators B: Chemical, 2020, 306, 127465. DOI: 10.1016/j.snb.2019.127465.
\end{itemize}
\end{sloppypar}

\subsection{Conference Presentations}
\begin{sloppypar}
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textit{Thermal Management System for a Fluidic Card in a Small Satellite Biological Payload}, Korean Institute of Electrical Engineers (KIEE) Autumn Conference, 2022.
    \item \textit{A Pipette with an Integrated pH Sensor for Liquid Sampling Applications}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2019.
    \item \textit{IoT System for Monitoring pH, Dissolved Oxygen, Temperature, and Electrical Conductivity in Liquids}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2018.
    \item \textit{Development Trends of Non-Invasive Glucose Sensor Technology}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2017.
\end{itemize}
\end{sloppypar}

\subsection{Seminar Presentations}
\begin{itemize}[leftmargin=0.5cm, itemsep=2pt, parsep=1pt]
    \item \textit{Bioprocessing in Space: Challenges and Opportunities for Pharmaceutical Manufacturing Beyond Earth}, Lowell Center for Space Science and Technology (LoCSST), UMass Lowell, 2025.
\end{itemize}

\vfill
\centering{References available upon request.}

\end{document}
