\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[letterpaper, margin=0.8in]{geometry}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[unicode]{hyperref}

\name{Saeyoung}{Kim}
\address{Cambridge, MA, USA}{}{}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}

\recipient{Hiring Team}{ASML\\San Diego, CA}
\date{\today}
\opening{Dear Hiring Team,}
\closing{Sincerely,}

\begin{document}

\makelettertitle

I'm interested in the Senior Test Technician position (J-00335596) in San Diego. I've spent most of my career building and testing electronics in cleanroom and controlled environments, and I think that experience translates well here.

At Hanwha Systems, I ran integration and test campaigns on military satellite flight hardware. That meant setting up test equipment, running procedures, tracking down anomalies, and writing up reports. Everything was tightly procedural with real deadlines, and when something failed, I had to figure out why and fix it.

My PhD work was similar but at a smaller scale. I designed circuits, fabricated sensors in a cleanroom, soldered and assembled prototypes, and tested everything with oscilloscopes, function generators, and custom fixtures. I got comfortable working with test equipment early on and never really stopped.

I like the idea of doing this kind of work on ASML's lithography systems. Happy to talk more about it. Thanks for your time.

\makeletterclosing

\end{document}
