\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[letterpaper, margin=0.8in]{geometry}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[unicode]{hyperref}

\name{Saeyoung}{Kim}
\address{Cambridge, MA, USA}{}{}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}

\recipient{Hiring Team}{Persimmon Technologies Corporation\\Bedford, MA}
\date{\today}
\opening{Dear Hiring Team,}
\closing{Sincerely,}

\begin{document}

\makelettertitle

I'm applying for the Robot Manufacturing Technician position. I have an engineering background, but what I actually want to do every day is build things with my hands. I'm looking for a role where I'm on the floor assembling hardware, not sitting at a desk. That's what drew me to this posting.

At Hanwha Systems, the best parts of my job were the days I spent in the cleanroom physically assembling satellite hardware. Precision mechanical assembly, torquing flight hardware, installing PCBAs into housings, routing cables and terminating connectors, troubleshooting builds when something didn't fit or didn't work. That hands-on work is what I'm good at and what I want to keep doing. I worked with controlled procedures, maintained build documentation and traceability records, and kept my workspace clean and organized to aerospace standards.

During my PhD, I did the same kind of thing at a smaller scale. PCB assembly and soldering, cleanroom fabrication with vacuum deposition and chemical processing, precision mechanical assembly of sensor hardware, and building test fixtures. Seven years of building things with my hands, testing them, fixing them, and building them again.

I know my resume has more degrees than a typical technician posting asks for. I'm not looking for a desk job that matches my credentials. I want to be the person putting robots together. That's the work I find satisfying, and I'm good at it.

I'm based in Cambridge, so Bedford is a short commute. My green card is currently pending, and I expect to have it in hand within the next few months. I'm happy to discuss timing directly.

\makeletterclosing

\end{document}
