\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\usepackage{xpatch}
\moderncvcolor{black} % Subtle, classic color
\AtBeginDocument{\definecolor{color2}{rgb}{0,0,0}} % Force first name black
\usepackage[letterpaper, margin=0.6in]{geometry}
\usepackage{xcolor} % Ensure color support
\usepackage{graphicx} % Support for images
\usepackage{fontspec} % Support for Unicode characters
\setmainfont{Times New Roman} % Set English font
% \newfontfamily\koreanfont{Noto Sans CJK KR} % Korean font (uncomment if needed)
\pagenumbering{arabic} % Ensure page numbering is defined
\usepackage[unicode]{hyperref} % Load hyperref after setting page numbering
\sloppy % Allow LaTeX to relax spacing issues
\usepackage{enumitem} % Allows list customization

\usepackage[english]{babel}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

%==================== PERSONAL INFO ====================%
\name{\textcolor{black}{Saeyoung}}{Kim}
\address{Cambridge, MA, USA}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}
\social[github]{PrimaryAnomaly}

\begin{document}

\makecvtitle
\vspace{-3em}

%==================== SUMMARY ====================%
\section{Professional Summary}
Hands-on Assembly, Integration, and Testing (AIT) engineer with 9+ years of experience building, testing, and validating complex space hardware across satellite systems, CubeSat payloads, and embedded sensing platforms. Performed functional and performance testing per documented procedures, diagnosed hardware anomalies, and incorporated engineering changes on flight and test hardware. Skilled in reading engineering drawings and schematics, operating precision measurement tools, and working with pressurized test systems. Proven track record of delivering high-quality results under tight deadlines in fast-moving, cross-functional team environments.

\section{Technical Skills}
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Hardware AIT}{Assembly, Integration, Functional/Performance Testing}
\cvitem{Electronics}{Circuit Design, PCB Layout, Soldering, System Integration}
\cvitem{CAD/Fabrication}{Fusion360, AutoCAD, KiCad, 3D Printing, CNC}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\cvitem{Instruments}{Calipers, Micrometers, Torque Wrenches, Multimeters, Oscilloscopes}
\cvitem{Software}{Python, C/C++, MATLAB, Git, Linux}
\cvitem{Methods}{Space Hardware AIT, Test Procedure Development, Anomaly Diagnosis}
\end{minipage}

%==================== EXPERIENCE ====================%
\section{Professional Experience}

\cventry{2025.07--Present}{\textbf{Postdoctoral Associate} | Process Monitoring and Test System Development}{University of Massachusetts Lowell}{Lowell, MA, USA}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Developed real-time quality monitoring systems for pharmaceutical manufacturing, validating 100+ production batches
    \item Built automated test and data acquisition pipelines for multi-day process cycles with quality prediction
    \item Collaborated across engineering and research teams to translate process requirements into validated technical tools
    \item Led deliverables for government-funded collaboration, coordinating across cross-functional stakeholders
\end{itemize}}

\cventry{2024.02--2025.05}{\textbf{AI\&T Engineer} | Satellite Assembly, Integration, and Testing}{Hanwha Systems}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Led assembly, integration, and testing (AIT) campaigns for military SAR satellite flight hardware
    \item Developed and executed functional and performance test procedures for hardware validation per engineering documentation
    \item Defined and executed Integrated Systems Test (IST) plans for Flight Model assembly through acceptance testing
    \item Designed Electrical Ground Support Equipment (EGSE) architecture and integration test configurations
    \item Diagnosed hardware anomalies during integration testing and recommended corrective actions to engineering
    \item Incorporated engineering changes into test procedures and hardware configurations across subsystem interfaces
    \item Read and interpreted engineering drawings, schematics, and equipment specifications for daily test operations
    \item Contributed to designing a high-throughput satellite manufacturing and AIT facility
\end{itemize}}

%==================== EDUCATION ====================%
\section{Education}
\cventry{2017.03--2024.02}{\textbf{PhD in Electrical Engineering} | CubeSat Hardware Development \& Sensor Integration}{Korea University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Secured and managed \$220K research grant for CubeSat biological payload hardware development
    \item Designed, fabricated, assembled, and tested multi-modal sensor suites for space flight applications using adhesives, solvents, and cleanroom chemicals
    \item Built and validated hardware prototypes through full cycle: circuit design, PCB layout, assembly, and functional testing
    \item Developed firmware in C/C++ for real-time sensor data acquisition and autonomous hardware operation
    \item Diagnosed and resolved hardware anomalies in networked electromechanical test systems
    \item Trained and mentored junior researchers on hardware assembly procedures and test equipment operation
    \item Published 2 first-author and 6 co-authored journal papers on electrochemical sensors, space payloads, and embedded systems
\end{itemize}}

\cventry{2013.03--2017.02}{\textbf{BSc in Mechanical Engineering}}{Konkuk University}{Seoul, South Korea}{}{
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item Conducted hands-on research in electrochemical sensor fabrication and hardware prototyping
    \item Gained experience in CAD modeling, reading mechanical drawings, PCB prototyping, and precision measurement
\end{itemize}}

%==================== PUBLICATIONS ====================%
\section{Publications}
\subsection{Journal Publications}
\begin{sloppypar} % Prevents underfull box errors
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textbf{\underline{Saeyoung Kim}}, Jaewon Lee, Kimia Babaei, Seonkgyu Yoon, "Digital Twins in Lyophilization: Advances in Pharmaceutical Process Development and Optimization," \textit{Biotechnology Advances}, 2026. (Manuscript in Preparation, Target Submission: Q1 2026)
    \item Jinhwee Kil, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "Investigation of thermal management strategies for biological CubeSat payloads," Acta Astronautica, 2024, Art. no. 228. DOI: 10.1016/j.actaastro.2024.11.059.
    \item \textbf{\underline{Kim, S.}}; Park, S.; Pak, J.J., "Multi-Modal Multi-Array Electrochemical and Optical Sensor Suite for a Biological CubeSat Payload," MDPI Sensors, 2024, 24, Art. no. 265. DOI: 10.3390/s24010265.
    \item Ji-Hoon Han, Sang Hyun Park, \textbf{\underline{Saeyoung Kim}}, James Jungho Pak, "A Performance Improvement of Enzyme-Based Electrochemical Lactate Sensor Fabricated by Electroplating Novel PdCu Mediator on a Laser Induced Graphene Electrode," Bioelectrochemistry, 2022, 148, 108259. DOI: 10.1016/j.bioelechem.2022.108259.
    \item \textbf{\underline{Saeyoung Kim}}, Ji-Hoon Han, Beelee Chua, James Jungho Pak, "A pH Sensing Pipette for Cross-Contamination Prevention in Industrial Fermentation," IEEE Transactions on Industrial Electronics, 2022, 69(7), 7461-7469. DOI: 10.1109/TIE.2021.3099251.
    \item S.D. Raut, N.M. Shinde, B.G. Ghule, \textbf{\underline{S. Kim}}, J.J. Pak, Q. Xia, R.S. Mane, "Room-Temperature Solution Processed Sharp-Edged Nanoshapes of," Chemical Engineering Journal, 2022, 433(2), 133627. DOI: 10.1016/j.cej.2021.133627.
    \item S.E. Jeong, \textbf{\underline{S. Kim}}, J.H. Han, J. Jungho Pak, "Simple Laser-Induced Graphene Fiber Electrode Fabrication for High-Performance Heavy-Metal Sensing," Microchemical Journal, 2022, 172, 106950. DOI: 10.1016/j.microc.2021.106950.
    \item Sanghoon Cho, Jungmo Jung, \textbf{\underline{Saeyoung Kim}}, James Pak, "Conduction Mechanism and Synaptic Behaviour of Interfacial Switching AlOσ-based RRAM," Semiconductor Science and Technology, 2020, 35(8), 085006. DOI: 10.1088/1361-6641/ab8d0e.
    \item Ji-Hoon Han, \textbf{\underline{Saeyoung Kim}}, Jaesung Choi, Sora Kang, Youngmi Kim Pak, James Jungho Pak, "Development of Multi-Well-Based Electrochemical Dissolved Oxygen Sensor Array," Sensors and Actuators B: Chemical, 2020, 306, 127465. DOI: 10.1016/j.snb.2019.127465.
\end{itemize}
\end{sloppypar}

\subsection{Conference Presentations}
\begin{sloppypar}
\begin{itemize}[leftmargin=1cm, itemsep=0pt, parsep=0pt]
    \item \textit{Thermal Management System for a Fluidic Card in a Small Satellite Biological Payload}, Korean Institute of Electrical Engineers (KIEE) Autumn Conference, 2022.
    \item \textit{A Pipette with an Integrated pH Sensor for Liquid Sampling Applications}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2019.
    \item \textit{IoT System for Monitoring pH, Dissolved Oxygen, Temperature, and Electrical Conductivity in Liquids}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2018.
    \item \textit{Development Trends of Non-Invasive Glucose Sensor Technology}, Korean Institute of Electrical Engineers (KIEE) Summer Conference, 2017.
\end{itemize}
\end{sloppypar}

\subsection{Seminar Presentations}
\begin{itemize}[leftmargin=0.5cm, itemsep=2pt, parsep=1pt]
    \item \textit{Bioprocessing in Space: Challenges and Opportunities for Pharmaceutical Manufacturing Beyond Earth}, Lowell Center for Space Science and Technology (LoCSST), UMass Lowell, 2025.
\end{itemize}

\vfill
\centering{References available upon request.}

\end{document}
