\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[letterpaper, margin=0.8in]{geometry}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[unicode]{hyperref}

\name{Saeyoung}{Kim}
\address{Cambridge, MA, USA}{}{}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}

\recipient{Hiring Team}{GreenSight Inc.\\Boston, MA}
\date{\today}
\opening{Dear Hiring Team,}
\closing{Sincerely,}

\begin{document}

\makelettertitle

I'm applying for the Senior Electrical Engineer position. I've spent the last several years designing electronics from scratch, building them with my own hands, and testing them until they work. The posting says you want someone comfortable rolling up their sleeves and tackling any electronic problem that comes up. That's how I've worked my entire career.

During my PhD, I owned the electrical design for a CubeSat sensor payload from start to finish. I drew schematics, laid out PCBs, soldered and reworked boards (through-hole and SMT), wrote MCU firmware in C/C++ for data acquisition over I2C, SPI, and UART, and then built the test setups to characterize everything with oscilloscopes, DMMs, and function generators. I went through multiple design-to-qualification cycles, writing test documentation each round and iterating based on what failed. That's seven years of doing exactly the kind of broad, hands-on electrical work this role describes.

At Hanwha Systems, I moved into systems integration for military satellite programs, where I designed EGSE architecture, developed acceptance test documentation, and spent most of my time debugging electronic hardware on the bench. When something failed, I traced it through schematics and firmware logs to find root cause and worked with the design teams to fix it.

I'll be upfront: my PCB design experience is in KiCad, not Altium. I've used it extensively and I'm confident I can pick up Altium quickly since the underlying concepts are the same. I also don't have specific experience with high-power systems (>100V / >1kW), though my fundamentals in circuit design and power electronics are solid.

I'm based in Cambridge, so Boston is an easy commute. My green card is currently pending, and I expect to have it in hand within the next few months. I'm happy to discuss timing directly.

\makeletterclosing

\end{document}
