\documentclass[letterpaper,11pt]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[letterpaper, margin=0.8in]{geometry}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[unicode]{hyperref}

\name{Saeyoung}{Kim}
\address{Cambridge, MA, USA}{}{}
\phone[mobile]{+1 (351) 322 5510}
\email{saeyoung\_kim@uml.edu}
\social[linkedin]{saeyoung-macx-kim}

\recipient{Hiring Team}{Tesla, Optimus Manufacturing\\Palo Alto, CA}
\date{\today}
\opening{Dear Hiring Team,}
\closing{Sincerely,}

\begin{document}

\makelettertitle

I'm applying for the Systems Engineer, Optimus Manufacturing position. I've spent the last few years taking electromechanical systems from early prototypes through integration and qualification, and that's essentially what this role is about at a much larger scale.

At Hanwha Systems, I worked on military satellite programs where I did hands-on mechanical assembly and electrical integration in cleanroom environments, wrote test and assembly procedures that technicians used on the floor, and fed manufacturing issues back to the design teams so they could fix things before the next build. I also helped define the facility architecture for a new high-throughput satellite production line. The work was fast, tightly scheduled, and involved constant coordination across mechanical, electrical, software, and program teams.

My PhD was a smaller-scale version of the same thing. I took a CubeSat sensor payload from concept through circuit design, PCB fabrication, cleanroom processing, mechanical assembly, and system-level testing. I went through multiple prototype revisions, adjusting the design each time based on what broke or didn't fit. That's where I learned to think about how design choices affect assembly and where problems actually show up when you try to build something.

I'm interested in this role because the problem is compelling: figuring out how to build a humanoid robot at scale. That's a manufacturing challenge I'd like to be part of solving.

Thanks for your time.

\makeletterclosing

\end{document}
